### 2021-04-13 conclusion.tex
Moved conclusion to its own section.

\begin{document}
\section{Related Work}
\subsubsection*{Deadlock freedom and progress}
Deadlock freedom and progress are well studied properties in the $\pi$-calculus.
For the `standard' typed $\pi$-calculus, an important line of work starts from Kobayashi's approach to deadlock freedom~\cite{kobayashi98}, where priorities are values from an abstract poset. Kobayashi~\cite{kobayashi06} simplifies the abstract poset to pairs of naturals, called \emph{obligations} and\emph{capabilities}. Padovani simplifies these further to a single natural, called a \emph{priority}~\cite{padovani14}, and adapts obligations/capabilities to session types~\cite{padovani13}.

@@

\subsubsection*{Ties with logic}
The correspondence between logic and types lays the foundation for functional programming~\cite{wadler15}.
Since its inception by Girard~\cite{girard87}, linear logic has been a candidate for a foundational correspondence for concurrent programs.
A~correspondence with linear $\pi$-calculus was established early on by Abramsky~\cite{abramsky94} and Bellin and Scott~\cite{bellinscott94}. Many years later, correspondences with the $\pi$-calculus with binary session types were proposed. Caires and Pfenning~\cite{cairespfenning10} propose a correspondence with dual intuitionistic linear logic, while Wadler~\cite{wadler14} proposes a correspondence with classical linear logic. Both guarantee deadlock freedom via their connection to logic, as a consequence of cut elimination.
Dardha and Gay~\cite{dardhagay18} integrate Kobayashi and Padovani's work on priorities~\cite{kobayashi06,padovani14} with CP, loosening its ties to linear logic in exchange for expressivity.
Dardha and P\'{e}rez~\cite{dardhaperez15} compare Kobayashi-style typing and CLL typing, and show that CLL corresponds to a subsystem of Kobayashi's where restriction is applied once.
Balzer~\etal~\cite{balzerpfenning17} introduce sharing, which breaks deadlock freedom.
They later restore deadlock freedom using priorities~\cite{balzertoninho19}.
Carbone~\etal~\cite{CarboneMSY15,carbonelindley16} give a logical view of MPST with a generalised duality.
Caires and P\'{e}rez~\cite{CairesP16} give a presentation of MPST in terms of binary session types and the use of a \emph{medium process} which guarantee protocol fidelity and deadlock freedom.
Their binary session types are rooted in linear logic following the propositions-as-sessions correspondences.
Ciobanu and Horne~\cite{CiobanuH15} gave the first propositions-as-sessions correspondence of MPST with the \emph{calculus of structures}~\cite{Guglielmi07} with global and local session types are inspired by Scribble, which determines whether local session types can be combined in a deadlock free manner.
Horne~\cite{Horne20} presents a system for subtyping and multiparty compatibility where compatible processes are race free and deadlock free using a propositions-as-sessions correspondence, similar to the approach in~\cite{CiobanuH15}, with a non-commutative extension of linear logic.

\subsubsection*{Conclusion and future work}
We answered our research question by presenting Priority GV, a~session-typed functional language which allows cyclic communication structures and uses priorities to ensure deadlock freedom. We showed its relation to Priority CP~\cite{dardhagay18} via an operational correspondence.

@@

\subsubsection*{Acknowledgement}
The authors would like to thank Simon Fowler, April Gon\c{c}alves, and Philip Wadler for their comments on the manuscript.

>>>>

\begin{document}

\section{Related Work}

\paragraph*{Deadlock freedom and progress}
Deadlock freedom and progress are well studied properties in the $\pi$-calculus.
For the `standard' typed $\pi$-calculus, an important line of work starts from Kobayashi's approach to deadlock freedom~\cite{kobayashi98}, where priorities are values from an abstract poset. Kobayashi~\cite{kobayashi06} simplifies the abstract poset to pairs of naturals, called \emph{obligations} and\emph{capabilities}. Padovani simplifies these further to a single natural, called a \emph{priority}~\cite{padovani14}, and adapts obligations/capabilities to session types~\cite{padovani13}.

@@

\paragraph*{Ties with logic}
The correspondence between logic and types lays the foundation for functional programming~\cite{wadler15}.
Since its inception by Girard~\cite{girard87}, linear logic has been a candidate for a foundational correspondence for concurrent programs.
A~correspondence with linear $\pi$-calculus was established early on by Abramsky~\cite{abramsky94} and Bellin and Scott~\cite{bellinscott94}. Many years later, correspondences with the $\pi$-calculus with binary session types were proposed. Caires and Pfenning~\cite{cairespfenning10} propose a correspondence with dual intuitionistic linear logic, while Wadler~\cite{wadler14} proposes a correspondence with classical linear logic. Both guarantee deadlock freedom via their connection to logic, as a consequence of cut elimination.
Dardha and Gay~\cite{dardhagay18} integrate Kobayashi and Padovani's work on priorities~\cite{kobayashi06,padovani14} with CP, loosening its ties to linear logic in exchange for expressivity.
Dardha and P\'{e}rez~\cite{dardhaperez15} compare Kobayashi-style typing and CLL typing, and show that CLL corresponds to a subsystem of Kobayashi's where restriction is applied once.
Balzer~\etal~\cite{balzerpfenning17} introduce sharing, which breaks deadlock freedom.
They later restore deadlock freedom using priorities~\cite{balzertoninho19}.
Carbone~\etal~\cite{CarboneMSY15,carbonelindley16} give a logical view of MPST with a generalised duality.
Caires and P\'{e}rez~\cite{CairesP16} give a presentation of MPST in terms of binary session types and the use of a \emph{medium process} which guarantee protocol fidelity and deadlock freedom.
Their binary session types are rooted in linear logic following the propositions-as-sessions correspondences.
Ciobanu and Horne~\cite{CiobanuH15} gave the first propositions-as-sessions correspondence of MPST with the \emph{calculus of structures}~\cite{Guglielmi07} with global and local session types are inspired by Scribble, which determines whether local session types can be combined in a deadlock free manner.
Horne~\cite{Horne20} presents a system for subtyping and multiparty compatibility where compatible processes are race free and deadlock free using a propositions-as-sessions correspondence, similar to the approach in~\cite{CiobanuH15}, with a non-commutative extension of linear logic.

\section{Conclusion and Future Work}
We answered our research question by presenting Priority GV, a~session-typed functional language which allows cyclic communication structures and uses priorities to ensure deadlock freedom. We showed its relation to Priority CP~\cite{dardhagay18} via an operational correspondence.

@@

\paragraph*{Acknowledgements}
The authors would like to thank Simon Fowler, April Gon\c{c}alves, and Philip Wadler for their comments on the manuscript.
